---
title: "Open Science (with R)"
subtitle: "<br/>"
author: "Alessandro Tomassini<br/><br/>Lena Dorfschmidt"
institute: "<br/>MPhil Basic and Translational Neuroscience"
date: "18.01.2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      titleSlideClass: [center, middle]
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

```


```{r use-logo, echo=FALSE}
xaringanExtra::use_logo("logo_uni.jpg",exclude_class = c( "hide-logo"), width = "200px")
```

# Open Science
```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
xaringanExtra::use_editable()
```
.panelset[
.panel[.panel-name[What?]
Some differences between using remark.js (left) and using **xaringan** (right):

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]


]

.panel[.panel-name[Why?]

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]
]

.panel[.panel-name[How?]

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]
]

.panel[.panel-name[References]
]
]

---
# Open Science: Pros vs Cons

.pull-left[
### &#x1F917; Pros

.can-edit.key-likes[
- Promotes rigor
]
]

.pull-right[
### &#x1F620; Cons

.can-edit.key-dislikes[
- Takes time
]
]

---
class:  center, middle

# Get Started

---

# RMarkdown

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```
---

# GitHub

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```
--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](https://slides.yihui.org/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---

# Open Science Framework

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

---

# Some tips

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

class: center, middle
# Questions?

---

# Now try your hands

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```

See the help page `?xaringan::moon_reader` for all possible options that you can use.

---



# R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

# HTML Widgets

I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.

Similarly, the Shiny mode (`runtime: shiny`) does not work. I might get these issues fixed in the future, but these are not of high priority to me. I never turn my presentation into a Shiny app. When I need to demonstrate more complicated examples, I just launch them separately. It is convenient to share slides with other people when they are plain HTML/JS applications.

See the next page for two HTML widgets.

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```

---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---

# Some Tips

- Do not forget to try the `yolo` option of `xaringan::moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        yolo: true
    ```

---


# Some Tips

- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.org/xaringan/incremental.html) for examples.

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          highlightLines: true
    ```

    See examples on the next page.

---

# Some Tips


.pull-left[
An example using a leading `*`:

    ```r
    if (TRUE) {
    ** message("Very important!")
    }
    ```
Output:
```r
if (TRUE) {
* message("Very important!")
}
```

This is invalid R code, so it is a plain fenced code block that is not executed.
]

.pull-right[
An example using `{{}}`:

````
`r ''````{r tidy=FALSE}
if (TRUE) {
*{{ message("Very important!") }}
}
```
````
Output:
```{r tidy=FALSE}
if (TRUE) {
{{ message("Very important!") }}
}
```

It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
]

---

# Some Tips

An example of using the trailing comment `#<<` to highlight lines:

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

Output:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---

# Some Tips

When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk. For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.

````md
`r ''````{r, highlight.output=c(1, 3)}
head(iris)
```
````

```{r, highlight.output=c(1, 3), echo=FALSE}
head(iris)
```

Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)

---

# Some Tips

- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).

- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.

- Then change the `chakra` option in YAML to point to this file, e.g.

    ```yaml
    output:
      xaringan::moon_reader:
        chakra: libs/remark-latest.min.js
    ```

- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally. The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.



---

class: center, middle

# Now try your hands!


